From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/analysis.tex
[ACL2020] Sect4+5: ResNetVGMN removed from tables

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|@{~}c|@{~}c@{~}|c@{~}c@{~}c@{~}c@{~}|c}
		\toprule
		&  & Hit & \multicolumn{4}{c@{~}|}{Human-like} & Off \\
		Model & GT  &  & SameObject &  OtherObject &  LowCount &  Related &   \\
		\midrule
		FRCNN$_{\text{VG1600}}$&VG &         74.8 &                13.7 &                  2.9 &              2.4 &              1.7 &          4.5 \\
		FRCNN$_{\text{MN442}}$&VG &         71.1 &                13.6 &                  3.4 &              2.0 &              2.6 &          7.4 \\
		\midrule
		FRCNN$_{\text{VG1600--VGMN}}$&MN &         80.7 &                 9.0 &                  2.0 &              1.8 &              3.4 &          3.3 \\
		\midrule
		ResNet101$_{\text{VGMN}}$&MN &         68.7 &                 9.9 &                  3.0 &              2.5 &              7.7 &          8.2 \\
		ResNet101$_{\text{MN442}}$&MN &         69.7 &                 9.9 &                  3.2 &              2.7 &              7.0 &          7.6 \\	
		ResNet101$_{\text{VGMN}}$&VG &         62.8 &                11.6 &                  2.1 &              3.2 &             10.3 &         10.1 \\
		ResNet101$_{\text{MN442}}$&VG &         63.8 &                11.9 &                  2.4 &              3.3 &              8.8 &          9.9 \\
		\bottomrule
	\end{tabular}
	\caption{Model results for different categories of errors. \label{tab:humanlike}}
\end{table*}

@@

\iffalse
\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll||rr|rrr}
\toprule
&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
                         model &  gt &  hit &  valid &  human-like &  related &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
        \midrule
 FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
         \midrule
     ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
\bottomrule
\end{tabular}

@@

\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll|rrr|rrr}
\toprule
&  & \multicolumn{3}{c|}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$0.9}\\
                         model &  GT &  hit &  human-like &  off &  hit &  human-like &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG &   94.8 &           2.6 &      2.6 &   63.6 &          30.9 &      5.5 \\
        FRCNN$_{\text{MN442}}$ &  VG &   89.6 &           4.2 &      6.2 &   60.7 &          31.3 &      8.0 \\
        \midrule
 FRCNN$_{\text{VG1600--VGMN}}$ &  MN &   94.5 &           4.2 &      1.3 &   72.9 &          22.7 &      4.4 \\
 \midrule
     ResNet101$_{\text{VGMN}}$ &  VG &   88.3 &           6.2 &      5.5 &   48.5 &          38.8 &     12.7 \\
     ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &           5.5 &      4.9 &   57.0 &          32.9 &     10.1 \\
    ResNet101$_{\text{MN442}}$ &  MN &   90.1 &           4.9 &      4.9 &   58.2 &          32.8 &      9.0 \\
    ResNet101$_{\text{MN442}}$ &  VG &   88.6 &           5.2 &      6.2 &   49.9 &          38.2 &     12.0 \\
\bottomrule
\end{tabular}
\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{human-like} error (less preferred name, synonym, hypernym/hyponym), or \textit{off} \label{tab:exp_errors_agreement}}
\end{table*}
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{l|l|c@{~}c@{~}c@{~}c}
		\toprule
		{Model} &  GT & visual &  linguistic &  box &  other \\
		\midrule
		FRCNN$_{\text{VG1600}}$ & VG &             4.3 &                 0.0 &                  95.7 &            0.0 \\
		FRCNN$_{\text{MN442}}$ & VG &             3.4 &                 0.0 &                  96.6 &            0.0 \\
		\midrule
		FRCNN$_{\text{VG1600--VGMN}}$ & MN &             6.7 &                 0.0 &                  93.3 &            0.0 \\
		\midrule
		ResNet101$_{\text{VGMN}}$ & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
		ResNet101$_{\text{MN442}}$ & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\
		ResNet101$_{\text{VGMN}}$ & VG &             5.6 &                 0.0 &                  94.4 &            0.0 \\
		ResNet101$_{\text{MN442}}$ & VG &             4.8 &                 0.0 &                  95.2 &            0.0 \\
		\bottomrule
	\end{tabular}
	\caption{Break-down of the instances (in \%) for which the models predicted an \textit{inadequate} name according to the type of inadequacy.  \label{tab:exp_inadequacy}}
\end{table}
\iffalse
\begin{figure}
	\centering
	\includegraphics[scale=.2]{images/2323938.jpg}
	\includegraphics[scale=.2]{images/2322259.jpg}
	\includegraphics[scale=.2]{images/2371657.jpg}

>>>>

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|@{~}c|@{~}c@{~}|c@{~}c@{~}c@{~}c@{~}|c}
		\toprule
		&  & Hit & \multicolumn{4}{c@{~}|}{Human-like} & Off \\
		Model & GT  &  & SameObject &  OtherObject &  LowCount &  Related &   \\
		\midrule
		FRCNN$_{\text{VG1600}}$&VG &         74.8 &                13.7 &                  2.9 &              2.4 &              1.7 &          4.5 \\
		FRCNN$_{\text{MN442}}$&VG &         71.1 &                13.6 &                  3.4 &              2.0 &              2.6 &          7.4 \\
		\midrule
		FRCNN$_{\text{VG1600--VGMN}}$&MN &         80.7 &                 9.0 &                  2.0 &              1.8 &              3.4 &          3.3 \\
		\midrule
		%ResNet101$_{\text{VGMN}}$&MN &         68.7 &                 9.9 &                  3.0 &              2.5 &              7.7 &          8.2 \\
		ResNet101$_{\text{MN442}}$&MN &         69.7 &                 9.9 &                  3.2 &              2.7 &              7.0 &          7.6 \\	
		ResNet101$_{\text{VGMN}}$&VG &         62.8 &                11.6 &                  2.1 &              3.2 &             10.3 &         10.1 \\
		ResNet101$_{\text{MN442}}$&VG &         63.8 &                11.9 &                  2.4 &              3.3 &              8.8 &          9.9 \\
		\bottomrule
	\end{tabular}
	\caption{Model results for different categories of errors. \label{tab:humanlike}}
\end{table*}

@@

\iffalse
\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll||rr|rrr}
\toprule
&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
                         model &  gt &  hit &  valid &  human-like &  related &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
        \midrule
 FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
         \midrule
         %ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
         ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
     	ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\

\bottomrule
\end{tabular}

@@

\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll|rrr|rrr}
\toprule
&  & \multicolumn{3}{c|}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$0.9}\\
                         model &  GT &  hit &  human-like &  off &  hit &  human-like &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG &   94.8 &           2.6 &      2.6 &   63.6 &          30.9 &      5.5 \\
        FRCNN$_{\text{MN442}}$ &  VG &   89.6 &           4.2 &      6.2 &   60.7 &          31.3 &      8.0 \\
        \midrule
 	FRCNN$_{\text{VG1600--VGMN}}$ &  MN &   94.5 &           4.2 &      1.3 &   72.9 &          22.7 &      4.4 \\
 \midrule
 %ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &           5.5 &      4.9 &   57.0 &          32.9 &     10.1 \\
 ResNet101$_{\text{MN442}}$ &  MN &   90.1 &           4.9 &      4.9 &   58.2 &          32.8 &      9.0 \\
     ResNet101$_{\text{VGMN}}$ &  VG &   88.3 &           6.2 &      5.5 &   48.5 &          38.8 &     12.7 \\
    ResNet101$_{\text{MN442}}$ &  VG &   88.6 &           5.2 &      6.2 &   49.9 &          38.2 &     12.0 \\
\bottomrule
\end{tabular}
\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{human-like} error (less preferred name, synonym, hypernym/hyponym), or \textit{off} \label{tab:exp_errors_agreement}}
\end{table*}
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{l|l|c@{~}c@{~}c@{~}c}
		\toprule
		{Model} &  GT & visual &  linguistic &  box &  other \\
		\midrule
		FRCNN$_{\text{VG1600}}$ & VG &             4.3 &                 0.0 &                  95.7 &            0.0 \\
		FRCNN$_{\text{MN442}}$ & VG &             3.4 &                 0.0 &                  96.6 &            0.0 \\
		\midrule
		FRCNN$_{\text{VG1600--VGMN}}$ & MN &             6.7 &                 0.0 &                  93.3 &            0.0 \\
		\midrule
		%ResNet101$_{\text{VGMN}}$ & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
		ResNet101$_{\text{MN442}}$ & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\
		ResNet101$_{\text{VGMN}}$ & VG &             5.6 &                 0.0 &                  94.4 &            0.0 \\
		ResNet101$_{\text{MN442}}$ & VG &             4.8 &                 0.0 &                  95.2 &            0.0 \\
		\bottomrule
	\end{tabular}
	\caption{Break-down of the instances (in \%) for which the models predicted an \textit{inadequate} name according to the type of inadequacy.  \label{tab:exp_inadequacy}}
\end{table}
\iffalse
\begin{figure}
	\centering
	\includegraphics[scale=.2]{images/2323938.jpg}
	\includegraphics[scale=.2]{images/2322259.jpg}
	\includegraphics[scale=.2]{images/2371657.jpg}
